---
title: 'Bios 7717: Bayesian Biostatistics, HW1'
author: "Li Zhang"
date: "Friday, September 19, 2014"
output: pdf_document
---
# Problem 1
  We will consider the specificity of the test \begin{quote}
\emph{$\theta$}\end{quote}, which is the probability
the test is negative when given to a Lyme negative individual. In the study, 25
patients with no history of Lyme disease were tested and 19 tested negative, for a
sample proportion of 19=25 = 0:76:Exact binomial test

data:  19 and 25

number of successes = 19, number of trials = 25, p-value = 0.01463
alternative hypothesis: true probability of success is not equal to 0.5
95 percent confidence interval:
 0.5487120 0.9064356
sample estimates:
probability of success 
                  0.76 
                  
```{binom.cloglog(19,25,conf.level=0.95,methods=exact)}
   method  x  n mean     lower     upper
1 cloglog 19 25 0.76 0.5420481 0.8842776

Large samle confience interval
  UL <- 0.76+1.96*sqrt(phat*(1-phat)/n)
  LL <- 0.76-1.96*sqrt(phat*(1-phat)/n)
  
 0.5925834, 0.9274166
 
 For interval estimation of a proportion, coverage probabilities tend to be too large for "exact" confidence intervals based on inverting the binomial test and too small for the interval based on inverting the Wald large-sample normal test (i.e., sample proportion ± z-score × estimated standard error). Wilson's suggestion of inverting the related score test with null rather than estimated standard error yields coverage probabilities close to nominal confidence levels, even for very small sample sizes. The 95% score interval has similar behavior as the adjusted Wald interval obtained after adding two "successes" and two "failures" to the sample. In elementary courses, with the score and adjusted Wald methods it is unnecessary to provide students with awkward sample size guidelines. 
 
   binom.confint(y, n, conf.level = 0.95)
          method  x  n mean     lower     upper
1  agresti-coull 19 25 0.76 0.5624805 0.8882596
2     asymptotic 19 25 0.76 0.5925865 0.9274135
3          bayes 19 25 0.75 0.5854415 0.9037771
4        cloglog 19 25 0.76 0.5420481 0.8842776
5          exact 19 25 0.76 0.5487120 0.9064356
6          logit 19 25 0.76 0.5584422 0.8880044
7         probit 19 25 0.76 0.5666202 0.8934027
8        profile 19 25 0.76 0.5724026 0.8967715
9            lrt 19 25 0.76 0.5724301 0.8968455
10     prop.test 19 25 0.76 0.5447916 0.8984194
11        wilson 19 25 0.76 0.5657032 0.8850369
```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

